Are kelp forests different? A comparison of kelp forests between contrasting

### 2018-10-10 paper_draft.Rmd
Update paper_draft.Rmd
first proper commit

---
title: Are kelp forests different? A comparison of kelp forests between contrasting
  study sites
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    fig_caption: yes
    fig_height: 5
    fig_width: 4
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

@@

\newpage
## Results

>>>>

---
title: Are kelp forests different? A comparison of kelp forests between contrasting
  study sites
output:
  pdf_document:
    toc: yes
  html_notebook:
    fig_caption: yes
    fig_height: 5
    fig_width: 4
    toc: yes
  html_document:
    df_print: paged
    toc: yes
  word_document:
    toc: yes
---

@@

\newpage

## Results

Intro explanation

```{r include=FALSE}

fauna_df <-  read.csv(file = "data/fauna.csv", sep = ";", check.names = FALSE)
flora_df <-  read.csv(file = "data/flora.csv", sep = ";", check.names = FALSE)
community_df <- read.csv(file = "data/community.csv", sep = ";", check.names = FALSE)

```

```{r message=FALSE, warning=FALSE, include=FALSE}

library(ggplot2)
library(reshape2)
library(vegan)
library(tidyverse)

```

## Community structure

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

fauna_lng <- melt(fauna_df, id.vars = c("site", "plot", "id"), value.name = "biomass", variable.name =  "species")

fauna_sum <- fauna_lng %>% 
  group_by(site, species) %>% 
  summarise(mean_biomass = mean(biomass, na.rm = T),
            min_biomass = min(biomass, na.rm = T),
            max_biomass = max(biomass, na.rm = T),
            range_biomass = range(biomass, na.rm = T)[2]-range(biomass, na.rm = T)[1],
            sd_biomass = sd(biomass, na.rm = T)) %>% 
  ungroup()

fauna_sum <- melt(fauna_sum, id.vars = c("site", "species"), value.name = "value")

plot_fauna <- ggplot(data = fauna_sum, aes(x= species, y = mean_biomass, color = site)) 
plot_fauna <- plot_fauna + geom_point()
plot_fauna <- plot_fauna + theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0))
plot_fauna <- plot_fauna + coord_flip()

flora_lng <- melt(flora_df, id.vars = c("site", "plot", "id"), value.name = "biomass", variable.name =  "species")

flora_sum <- flora_lng %>% 
  group_by(site, species) %>% 
  summarise(mean_biomass = mean(biomass, na.rm = T))%>% 
  ungroup()

flora_sum <- melt(flora_sum, id.vars = c("site", "species"), value.name = "mean_biomass")

plot_flora <- ggplot(data = flora_sum, aes(x= species, y = mean_biomass, color = site)) 
plot_flora <- plot_flora + geom_point()
plot_flora <- plot_flora + theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0))
plot_flora <- plot_flora + coord_flip()

```
